method

### 2022-02-21 06_Paper/ER-ED/method.Rmd
added abbr. EMG
added renv

```{r import, echo=FALSE, message=FALSE, warning=FALSE}
# import ER ratings and ER discounting data into lists

datalist_ER = lapply(list.files(here("04_RawData", "pilot", "ER-ED/logfiles"), pattern = '*_ER.*csv', full.names = TRUE),
                          read.csv, stringsAsFactors = FALSE, header = TRUE)

datalist_ED = lapply(list.files(here("04_RawData", "pilot", "ER-ED/logfiles"), pattern = '*_ED.*csv', full.names = TRUE),
                          read.csv, stringsAsFactors = FALSE, header = TRUE)

# new empty frame to store files into
data_ER = data.frame(ID = character(), block = character(), arousal = double(), 
                     effort = double(), trigger = double(), trigger_reg = double())

data_ED = data.frame(ID = character(), step = double(), choice = character(),
                     LBvalue = double(), LBlevel = double(), RBvalue = double(), RBlevel = double())

data_choice = data.frame(ID = character(), choice = double())

# store arousal and effort ratings in data_ER frame
for (i in 1:length(datalist_ER)) {

  tmp = data.frame(datalist_ER[[i]][["participant"]], 
                   datalist_ER[[i]][["instr_1"]], 
                   datalist_ER[[i]][["slider_arousal.response"]], 
                   datalist_ER[[i]][["slider_effort.response"]],
                   datalist_ER[[i]][["TriggerBlockView"]],
                   datalist_ER[[i]][["TriggerBlockReg"]])
  colnames(tmp) = names(data_ER)
  tmp = tmp[(!is.na(tmp$arousal)), ]

  data_ER = rbind(tmp, data_ER)

}

rownames(data_ER) = 1:nrow(data_ER)

# loop to store trigger in one column

for (i in 1:nrow(data_ER)) {
  if (is.na(data_ER$trigger[i])) {
    data_ER$trigger[i] = data_ER$trigger_reg[i]
  }

  if (is.na(data_ER$trigger[i])) {
    data_ER$trigger[i] = 26
  }
}

# delete old column

data_ER$trigger_reg = NULL

# loop to correct block indicator

data_ER$block[data_ER$trigger == 21] <- "1_view_neu"
data_ER$block[data_ER$trigger == 22] <- "2_view_neg"
data_ER$block[data_ER$trigger == 23] <- "3_distraction"
data_ER$block[data_ER$trigger == 24] <- "4_distancing"
data_ER$block[data_ER$trigger == 25] <- "5_suppression"
data_ER$block[data_ER$trigger == 26] <- "6_choice"

# store ER choice in data_choice frame

for (i in 1:length(datalist_ER)) {
  tmp = data.frame(datalist_ER[[i]][["participant"]], datalist_ER[[i]][["resp_choice.keys"]])
  colnames(tmp) = names(data_choice)
  tmp = tmp[(!is.na(tmp$choice)), ]

  data_choice = rbind(tmp, data_choice)
}

# store ED data in data_ED frame
#for (i in 1:length(datalist_ED)) {

#  tmp = data.frame(datalist_ED[[i]][["participant"]][2:length(datalist_ED[[i]][["participant"]])],
#                   datalist_ED[[i]][["EDround.thisN"]][2:length(datalist_ED[[i]][["EDround.thisN"]])],
#                   datalist_ED[[i]][["EDclick.clicked_name"]][2:length(datalist_ED[[i]][["EDclick.clicked_name"]])],
#                   datalist_ED[[i]][["EDleftbutton.value"]][2:length(datalist_ED[[i]][["EDleftbutton.value"]])],
#                   datalist_ED[[i]][["EDleftbutton.nback"]][2:length(datalist_ED[[i]][["EDleftbutton.nback"]])],
#                   datalist_ED[[i]][["EDrightbutton.value"]][2:length(datalist_ED[[i]][["EDrightbutton.value"]])],
#                   datalist_ED[[i]][["EDrightbutton.nback"]][2:length(datalist_ED[[i]][["EDrightbutton.nback"]])])

#  colnames(tmp) = names(data_ED)
#  data_ED = rbind(data_ED, tmp)
#}

# import EMG data

datalist_EMG <- lapply(list.files(here("04_RawData", "pilot", "ER-ED", "EMG", "analysis"), pattern = '*_Peaks.txt', full.names = TRUE),
                          read.table, stringsAsFactors = FALSE, header = TRUE)
datalist_EMG_Marker <- lapply(list.files(here("04_RawData", "pilot", "ER-ED", "EMG", "analysis"), pattern = "*.Markers", full.names = TRUE),
                              read.table, stringsAsFactors = FALSE, header = TRUE, skip = 1, row.names = NULL, sep = ",")

# new empty frame to store files into
data_EMG = data.frame(ID = character(), trigger = double(), Corr = double(), 
                     Lev = double())

# store EMG data in data_EMG frame
for (i in 1:length(datalist_EMG)) {

  tmp = data.frame(datalist_EMG[[i]][["Filename"]], 
                   datalist_EMG_Marker[[i]][["Description"]], 
                   datalist_EMG[[i]][["T0T6000Corr.ASNM"]], 
                   datalist_EMG[[i]][["T0T6000Lev.ASNM"]])
  colnames(tmp) = names(data_EMG)

  data_EMG = rbind(tmp, data_EMG)

}

# create variable "block"

data_EMG$block[data_EMG$trigger == " S 21"] <- "1_view_neu"
data_EMG$block[data_EMG$trigger == " S 22"] <- "2_view_neg"
data_EMG$block[data_EMG$trigger == " S 23"] <- "3_distraction"
data_EMG$block[data_EMG$trigger == " S 24"] <- "4_distancing"
data_EMG$block[data_EMG$trigger == " S 25"] <- "5_suppression"
data_EMG$block[data_EMG$trigger == " S 26"] <- "6_choice"

# import questionnaire df

data_quest = read.csv(here("04_RawData", "pilot", "ER-ED", "dfs", "df_quest.csv"), sep = ",")

```

```{r statistics, echo=FALSE, message=FALSE, warning=FALSE}
## Subjective arousal

# ANOVA subjective arousal ratings
# View condition

Ratings_view <- data_ER %>%
  subset(data_ER$block == "1_view_neu" | data_ER$block == "2_view_neg")
Ratings_view$block <- as.factor(Ratings_view$block)

SubjArousalView_aov <- afex::aov_ez(data = Ratings_view,
                               id = "ID",
                               dv = "arousal",
                               within = "block",
                               fun_aggregate = mean,
                               include_aov = TRUE)

# compute posthoc tests for within measures
SubjArousalView_emm <- emmeans::emmeans(SubjArousalView_aov$aov, specs = "block")

SubjArousalView_con <- as.data.frame(pairs(SubjArousalView_emm, adjust = "bonferroni"))

# Bayes Factors
SubjArousalView_BF <- BayesFactor::anovaBF(formula = arousal ~ block,
                                           data = Ratings_view,
                                           progress = FALSE)
SubjArousalView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_view$arousal[Ratings_view$block == "1_view_neu"],
                                                                        y = Ratings_view$arousal[Ratings_view$block == "2_view_neg"],
                                                                        progress = FALSE, paired = TRUE))$bf

SubjArousalView_con <- cbind(SubjArousalView_con,
                             format(effectsize::t_to_eta2(t = SubjArousalView_con$t.ratio,
                                                          df_error = SubjArousalView_con$df,
                                                          ci = 0.95),
                                                          digits = 2))

colnames(SubjArousalView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
# rename contrast for table
SubjArousalView_con[1,1] <- "$View_{neutral} - View_{negative}$"

# Figure to visualize arousal ratings

# figure
FigSubjArousalViewPilot=ggplot2::ggplot(Ratings_view, aes(x = block, y = arousal))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Active viewing", 
                   limits = c("1_view_neu", "2_view_neg"),
                   labels = c("Neutral", "Negative"))+
  geom_jitter(size = 0.4)+
  labs(y = "Arousal Rating")

# View neg and regulate conditions

Ratings_reg <- data_ER %>%
  subset(data_ER$block != "1_view_neu" & data_ER$block != "6_choice")
Ratings_reg$block <- as.factor(Ratings_reg$block)

SubjArousalReg_aov <- afex::aov_ez(data = Ratings_reg,
                              id = "ID",
                              dv = "arousal",
                              within = "block",
                              fun_aggregate = mean,
                              include_aov = TRUE)

# compute posthoc tests for within measures
SubjArousalReg_emm <- emmeans::emmeans(SubjArousalReg_aov$aov, specs = "block")

SubjArousalReg_con <- as.data.frame(pairs(SubjArousalReg_emm, adjust = "bonferroni"))

# Bayes Factors
SubjArousalReg_BF <- BayesFactor::anovaBF(formula = arousal ~ block,
                                          data = Ratings_reg,
                                          progress = FALSE)

SubjArousalReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "2_view_neg"],
                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "3_distraction"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "2_view_neg"],
                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "4_distancing"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "2_view_neg"],
                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "5_suppression"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "3_distraction"],
                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "4_distancing"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "3_distraction"],
                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "5_suppression"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "4_distancing"],
                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "5_suppression"],
                                                                         progress = FALSE, paired = TRUE))$bf)

SubjArousalReg_con <- cbind(SubjArousalReg_con,
                            format(effectsize::t_to_eta2(t = SubjArousalReg_con$t.ratio,
                                                         df_error = SubjArousalReg_con$df,
                                                         ci = 0.95),
                                   digits = 2))

colnames(SubjArousalReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")

SubjArousalReg_con[1,1] <- "$View_{negative} - Distraction$"
SubjArousalReg_con[2,1] <- "$View_{negative} - Distancing$"
SubjArousalReg_con[3,1] <- "$View_{negative} - Suppression$"
SubjArousalReg_con[4,1] <- "$Distraction - Distancing$"
SubjArousalReg_con[5,1] <- "$Distraction - Suppression$"
SubjArousalReg_con[6,1] <- "$Distancing - Suppression$"

# Figure to visualize arousal ratings

# figure
FigSubjArousalRegPilot <- ggplot2::ggplot(Ratings_reg, aes(x = block, y = arousal))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("2_view_neg", "3_distraction", "4_distancing", "5_suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Arousal Rating")

## Subjective effort

SubjEffort_aov <- afex::aov_ez(data = Ratings_reg,
                          id = "ID",
                          dv = "effort",
                          within = "block",
                          fun_aggregate = mean,
                          include_aov = TRUE)

# compute posthoc tests for within measure
SubjEffort_emm <- emmeans::emmeans(SubjEffort_aov$aov, specs = "block")

SubjEffort_con <- as.data.frame(pairs(SubjEffort_emm, adjust = "bonferroni"))

# Bayes Factors
SubjEffort_BF <- BayesFactor::anovaBF(formula = effort ~ block,
                                           data = Ratings_reg,
                                           progress = FALSE)

SubjEffort_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"],
                                                                     y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"],
                                                                     y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"],
                                                                     y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],
                                                                     y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],
                                                                     y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],
                                                                     y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],
                                                                     progress = FALSE, paired = TRUE))$bf)

SubjEffort_con <- cbind(SubjEffort_con,
                        format(effectsize::t_to_eta2(t = SubjEffort_con$t.ratio,
                                                         df_error = SubjEffort_con$df,
                                                         ci = 0.95),
                               digits = 2))

colnames(SubjEffort_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")

SubjEffort_con[1,1] <- "$View_{negative} - Distancing$"
SubjEffort_con[2,1] <- "$View_{negative} - Distraction$"
SubjEffort_con[3,1] <- "$View_{negative} - Suppression$"
SubjEffort_con[4,1] <- "$Distraction - Distancing$"
SubjEffort_con[5,1] <- "$Distraction - Suppression$"
SubjEffort_con[6,1] <- "$Distancing - Suppression$"

# Figure to visualize effort ratings
# figure
FigSubjEffortPilot = ggplot2::ggplot(Ratings_reg, aes(x = block, y = effort))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("2_view_neg", "3_distraction", "4_distancing", "5_suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Effort Rating")

### EMG

# effect of valence on EMG
# corrugator

EMG_view <- data_EMG %>%
  subset(data_EMG$block == "1_view_neu" | data_EMG$block == "2_view_neg")
EMG_view$block <- as.factor(EMG_view$block)

EMGCorrView_aov <- afex::aov_ez(data = EMG_view,
                               id = "ID",
                               dv = "Corr",
                               within = "block",
                               fun_aggregate = mean,
                               include_aov = TRUE)

# compute posthoc tests for within measures
EMGCorrView_emm <- emmeans::emmeans(EMGCorrView_aov$aov, specs = "block")

EMGCorrView_con <- as.data.frame(pairs(EMGCorrView_emm, adjust = "bonferroni"))

# Bayes Factors
EMGCorrView_BF <- BayesFactor::anovaBF(formula = Corr ~ block,
                                       data = EMG_view,
                                       progress = FALSE)
EMGCorrView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Corr[EMG_view$block == "1_view_neu"],
                                                                    y = EMG_view$Corr[EMG_view$block == "2_view_neg"],
                                                                    progress = FALSE, paired = TRUE))$bf

EMGCorrView_con <- cbind(EMGCorrView_con,
                         format(effectsize::t_to_eta2(t = EMGCorrView_con$t.ratio,
                                                          df_error = EMGCorrView_con$df,
                                                          ci = 0.95),
                                                          digits = 2))

colnames(EMGCorrView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
# rename contrast for table
EMGCorrView_con[1,1] <- "$View_{neutral} - View_{negative}$"

# Figure to visualize arousal ratings

# figure
FigEMGCorrViewPilot=ggplot2::ggplot(EMG_view, aes(x = block, y = Corr))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Active viewing", 
                   limits = c("1_view_neu", "2_view_neg"),
                   labels = c("Neutral", "Negative"))+
  geom_jitter(size = 0.4)+
  labs(y = "Corrugator activity")

# levator

EMGLevView_aov <- afex::aov_ez(data = EMG_view,
                               id = "ID",
                               dv = "Lev",
                               within = "block",
                               fun_aggregate = mean,
                               include_aov = TRUE)

# compute posthoc tests for within measures
EMGLevView_emm <- emmeans::emmeans(EMGLevView_aov$aov, specs = "block")

EMGLevView_con <- as.data.frame(pairs(EMGLevView_emm, adjust = "bonferroni"))

# Bayes Factors
EMGLevView_BF <- BayesFactor::anovaBF(formula = Lev ~ block,
                                       data = EMG_view,
                                       progress = FALSE)
EMGLevView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Lev[EMG_view$block == "1_view_neu"],
                                                                   y = EMG_view$Lev[EMG_view$block == "2_view_neg"],
                                                                   progress = FALSE, paired = TRUE))$bf

EMGLevView_con <- cbind(EMGLevView_con,
                        format(effectsize::t_to_eta2(t = EMGLevView_con$t.ratio,
                                                     df_error = EMGLevView_con$df,
                                                     ci = 0.95),
                                                     digits = 2))

colnames(EMGLevView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
# rename contrast for table
EMGLevView_con[1,1] <- "$View_{neutral} - View_{negative}$"

# Figure to visualize arousal ratings

# figure
FigEMGLevViewPilot=ggplot2::ggplot(EMG_view, aes(x = block, y = Lev))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Active viewing", 
                   limits = c("1_view_neu", "2_view_neg"),
                   labels = c("Neutral", "Negative"))+
  geom_jitter(size = 0.4)+
  labs(y = "Levator activity")

# effect of strategy on EMG

EMG_reg <- data_EMG %>%
  subset(data_EMG$block != "1_view_neu" & data_EMG$block != "6_choice")
EMG_reg$block <- as.factor(EMG_reg$block)

# corrugator
EMGCorrReg_aov <- afex::aov_ez(data = EMG_reg,
                              id = "ID",
                              dv = "Corr",
                              within = "block",
                              fun_aggregate = mean,
                              include_aov = TRUE)

# compute posthoc tests for within measures
EMGCorrReg_emm <- emmeans::emmeans(EMGCorrReg_aov$aov, specs = "block")

EMGCorrReg_con <- as.data.frame(pairs(EMGCorrReg_emm, adjust = "bonferroni"))

# Bayes Factors
EMGCorrReg_BF <- BayesFactor::anovaBF(formula = Corr ~ block,
                                      data = EMG_reg,
                                      progress = FALSE)

EMGCorrReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
                                                                     y = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
                                                                     y = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
                                                                     y = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
                                                                     progress = FALSE, paired = TRUE))$bf)

EMGCorrReg_con <- cbind(EMGCorrReg_con,
                        format(effectsize::t_to_eta2(t = EMGCorrReg_con$t.ratio,
                                                     df_error = EMGCorrReg_con$df,
                                                     ci = 0.95),digits = 2))

colnames(EMGCorrReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")

EMGCorrReg_con[1,1] <- "$View_{negative} - Distraction$"
EMGCorrReg_con[2,1] <- "$View_{negative} - Distancing$"
EMGCorrReg_con[3,1] <- "$View_{negative} - Suppression$"
EMGCorrReg_con[4,1] <- "$Distraction - Distancing$"
EMGCorrReg_con[5,1] <- "$Distraction - Suppression$"
EMGCorrReg_con[6,1] <- "$Distancing - Suppression$"

# Figure to visualize arousal ratings

# figure
FigEMGCorrRegPilot <- ggplot2::ggplot(EMG_reg, aes(x = block, y = Corr))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("2_view_neg", "3_distraction", "4_distancing", "5_suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Corrugator activity")

# levator

EMGLevReg_aov <- afex::aov_ez(data = EMG_reg,
                              id = "ID",
                              dv = "Lev",
                              within = "block",
                              fun_aggregate = mean,
                              include_aov = TRUE)

# compute posthoc tests for within measures
EMGLevReg_emm <- emmeans::emmeans(EMGLevReg_aov$aov, specs = "block")

EMGLevReg_con <- as.data.frame(pairs(EMGLevReg_emm, adjust = "bonferroni"))

# Bayes Factors
EMGLevReg_BF <- BayesFactor::anovaBF(formula = Lev ~ block,
                                      data = EMG_reg,
                                      progress = FALSE)

EMGLevReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "2_view_neg"],
                                                                    y = EMG_reg$Lev[EMG_reg$block == "3_distraction"],
                                                                    progress = FALSE, paired = TRUE))$bf,
                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "2_view_neg"],
                                                                    y = EMG_reg$Lev[EMG_reg$block == "4_distancing"],
                                                                    progress = FALSE, paired = TRUE))$bf,
                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "2_view_neg"],
                                                                    y = EMG_reg$Lev[EMG_reg$block == "5_suppression"],
                                                                    progress = FALSE, paired = TRUE))$bf,
                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "3_distraction"],
                                                                    y = EMG_reg$Lev[EMG_reg$block == "4_distancing"],
                                                                    progress = FALSE, paired = TRUE))$bf,
                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "3_distraction"],
                                                                    y = EMG_reg$Lev[EMG_reg$block == "5_suppression"],
                                                                    progress = FALSE, paired = TRUE))$bf,
                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "4_distancing"],
                                                                    y = EMG_reg$Lev[EMG_reg$block == "5_suppression"],
                                                                    progress = FALSE, paired = TRUE))$bf)

EMGLevReg_con <- cbind(EMGLevReg_con,
                       format(effectsize::t_to_eta2(t = EMGLevReg_con$t.ratio,
                                                    df_error = EMGLevReg_con$df,
                                                    ci = 0.95),digits = 2))

colnames(EMGLevReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")

EMGLevReg_con[1,1] <- "$View_{negative} - Distraction$"
EMGLevReg_con[2,1] <- "$View_{negative} - Distancing$"
EMGLevReg_con[3,1] <- "$View_{negative} - Suppression$"
EMGLevReg_con[4,1] <- "$Distraction - Distancing$"
EMGLevReg_con[5,1] <- "$Distraction - Suppression$"
EMGLevReg_con[6,1] <- "$Distancing - Suppression$"

# Figure to visualize arousal ratings

# figure
FigEMGLevRegPilot <- ggplot2::ggplot(EMG_reg, aes(x = block, y = Lev))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("2_view_neg", "3_distraction", "4_distancing", "5_suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Levator activity")

```

@@

Young, healthy participants (aged 18 to 30 years) will be recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden.
Participants will be invited to compete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
The study consists of two lab sessions, which take place in a shielded cabin with constant lighting.
Before each session, participants receive information about the respective experimental procedure and provide informed consent.
At the beginning of the first session participants fill out a demographic questionnaire and complete an n-Back task with the levels one to four.
Then, they complete an effort discounting (ED) procedure on screen, followed by a random repetition of one n-back level.
The second session, containing the ER paradigm, takes place exactly one week after session one.
Participants provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
A brief training ensures that all participants are able to implement the ER strategies.
Next, electrodes to measure EMG <!-- Has abbrev. EMG already are been introduced? -->being attached and the ER paradigm is conducted.
Participants receive 30.00€ or course credit as compensation.
Study data are being collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].

>>>>

@@

Young, healthy participants (aged 18 to 30 years) will be recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden.
Participants will be invited to compete an online survey containing different questionnaires to assess broad and narrow personality traits and measures of well-being.
The study consists of two lab sessions, which take place in a shielded cabin with constant lighting.
Before each session, participants receive information about the respective experimental procedure and provide informed consent.
At the beginning of the first session participants fill out a demographic questionnaire and complete an n-Back task with the levels one to four.
Then, they complete an effort discounting (ED) procedure on screen, followed by a random repetition of one n-back level.
The second session, containing the ER paradigm, takes place exactly one week after session one.
Participants provide informed consent and receive written instructions on the ER paradigm and ER strategies that they should apply.
A brief training ensures that all participants are able to implement the ER strategies.
Next, electrodes to measure EMG being attached and the ER paradigm is conducted.
Participants receive 30.00€ or course credit as compensation.
Study data are being collected and managed using REDCap electronic data capture tools hosted at Technische Universität Dresden [@Harris2009; @Harris2019].
